Hardware-accelerated Rendering of Intersecting Volumes using Boolean Operations

### 2013-04-22 paper.tex
Mention that in both approaches passes must start with results of previous pass
Fixed using 'primary-coords-texture' and 'secondary-coords-texture' in some places

@@

\begin{Verbatim}[fontsize=\small]
  <texture id="first-volume-texture" file="first.vlb">
  <texture id="second-volume-texture" file="second.vlb">
  <texture id="primary-coords-texture" width="768" height="768">
  <texture id="secondary-coords-texture" width="768" height="768">
  <texture id="results-texture" width="768" height="768">
\end{Verbatim}

@@

\begin{Verbatim}[fontsize=\small]
  <cull faces="front" />
  <framebuffer>
    <attachment usage="color" link="primary-coords-texture" />
    <use program="primary-coords-program">
      <instance of="cube-1-group" />
    </use>
  </framebuffer>
  <framebuffer>
    <attachment usage="color" link="results-texture" />
    <use program="first-pass-program">
      <booleanAnd id="intersection" of="cube-1 cube-2" />
    </use>
  </framebuffer>
\end{Verbatim}

@@

\begin{Verbatim}[fontsize=\small]
  <blend enabled="true" />
  <depth function="less" />
  <sort>
    <group>
      <framebuffer>
        <attachment usage="color" link="primary-coords-texture" />
        <use program="primary-coords-program">
          <cull mode="front" />
          <instance of="cube-1-group" />
        </use>
      </framebuffer>
      <use program="kruger-program">
        <cull faces="back" />
        <group id="cube-1-group">
          <translate x="-1">
            <cube id="cube-1" />
          </translate>
        </group>
      </use>
    </group>
    <group>
      <framebuffer>
        <attachment usage="color" link="coords-texture-2" />
        <use program="primary-coords-program">
          <cull mode="front" />
          <instance of="cube-2-group" />
        </use>
      </framebuffer>
      <use program="kruger-program">
        <cull mode="back" />
        <group id="cube-2-group">
          <translate x="+1">
            <cube id="cube-2" />
          </translate>
        </group>
      </use>
    </group>
  </sort>
\end{Verbatim}

>>>>

In addition, both approaches use multiple passes.  To blend the samples
correctly between passes, each pass must start with the results of the previous
pass.  The results of all the passes cannot be simply blended together
afterwards.

@@

\begin{Verbatim}[fontsize=\small]
  <texture id="first-volume-texture" file="first.vlb">
  <texture id="second-volume-texture" file="second.vlb">
  <texture id="coords-texture-1" width="768" height="768">
  <texture id="coords-texture-2" width="768" height="768">
  <texture id="results-texture" width="768" height="768">
\end{Verbatim}

@@

\begin{Verbatim}[fontsize=\small]
  <cull faces="front" />
  <framebuffer>
    <attachment usage="color" link="coords-texture-1" />
    <use program="primary-coords-program">
      <instance of="cube-1-group" />
    </use>
  </framebuffer>
  <framebuffer>
    <attachment usage="color" link="results-texture" />
    <use program="first-pass-program">
      <booleanAnd id="intersection" of="cube-1 cube-2" />
    </use>
  </framebuffer>
\end{Verbatim}

@@

\begin{Verbatim}[fontsize=\small]
  <blend enabled="true" />
  <depth function="less" />
  <sort>
    <group>
      <framebuffer>
        <attachment usage="color" link="coords-texture-1" />
        <use program="primary-coords-program">
          <cull mode="front" />
          <instance of="cube-1-group" />
        </use>
      </framebuffer>
      <use program="kruger-program">
        <cull faces="back" />
        <group id="cube-1-group">
          <translate x="-1">
            <cube id="cube-1" />
          </translate>
        </group>
      </use>
    </group>
    <group>
      <framebuffer>
        <attachment usage="color" link="coords-texture-2" />
        <use program="primary-coords-program">
          <cull mode="front" />
          <instance of="cube-2-group" />
        </use>
      </framebuffer>
      <use program="kruger-program">
        <cull mode="back" />
        <group id="cube-2-group">
          <translate x="+1">
            <cube id="cube-2" />
          </translate>
        </group>
      </use>
    </group>
  </sort>
\end{Verbatim}
